Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-30 draft/paper1_rachel.tex
ICL disucssion

@@

%% ------------------------------------------------------------------------------------ %% 
\subsection{Stellar Halo and Intra-cluster Light}

    Finally, we emphasize that in this work, we do not attempt  to  disentangle the galaxy light from any ``intra-cluster'' light component (ICL; e.g. 
    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}). Instead, we adopt the view that the light of the main galaxy and the 
    ``intra-cluster''component share a smooth and continuous distribution.

    In practice, reliable isolation of a physically meaningful ICL component using 
    photometry alone is extremely difficult, if not impossible. 
    More importantly, the majority of massive galaxies in our samples are not considered 
    as the BCG of a cluster (\mhalo{}$\simgt 10^{14}M_{\star}$) \alexie{CHECK}. 
    Only a small fraction of the BCGs in the \rbcg{} sample belong to very 
    massive clusters where the strongest photometric evidence of an ICL component is 
    often found (\mhalo{}$\simgt 10^{15}M_{\star}$, e.g. \citealt{Presotto2014, 
    Burke2015}). The virgo cluster is a good  local analog of the typical galaxy in our sample.

    Ultra-deep images show that the stellar halo of the BCG smoothly extends beyond 
    100 kpc, while the ICL only becomes important outside that radius and is dominated 
    by many individual tidal features (e.g. \citealt{Mihos2016}).
    Therefore, it is highly unlikely that out main results are driven by the ICL component. \alexie{I'm not sure I agree with these statements. What is the ICL anyway?}

    At the imaging depth of HSC and out to 100 kpc, the \mden{} profiles of massive 
    galaxies vary smoothly and we find no evidence for a distinctive ICL component. 
    Although the rising stellar velocity dispersion in the outskirt of massive BCG
    has been used as evidence of a kinematically separated ICL component (e.g. 
    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}), 
    we think it is reasonable to treat the stellar halo of BCG and potential ICL as 
    an integrated component. 
    They both carry important information regarding the assembly of central galaxy 
    and its dark matter halo. 
    In recent years, we can start to investigate the origin and evolution of ICL using 
    simulations where physical separation of ICL is possible
    (e.g. \citealt{SommerLarsen2005, Murante2007, Martel2012, Cui2014, Cooper2015, 
    Harris2017}). 
    It will be interesting to perform detailed comparisons between these simulations 
    and deep HSC observations to look into the contributions from different stellar 
    components to the halo of massive galaxy.

>>>>

    Finally, we emphasize that in this work, we do not attempt to disentangle the 
    galaxy light from any ``intra-cluster'' light component (ICL; e.g. 
    \citealt{Carlberg1997, Lin2004, Gonzalez2005, Mihos2005}). 
    Although the rising stellar velocity dispersion in the outskirt of massive BCG
    hints a kinematically separated ICL component (e.g. 
    \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}),
    it is extremely difficult to reliably isolate them photometrically.
    Moreover, both the stellar halo of main galaxy and the ICL component carry 
    important information regarding the assembly history of central galaxy and its 
    dark matter halo. 
    Therefore, we adopt the view that the light of the main galaxy and the 
    ICL component share a smooth and continuous distribution.

    % In practice, reliable isolation of a physically meaningful ICL component using 
    % photometry alone is extremely difficult, if not impossible. 
    % More importantly, the majority of massive galaxies in our samples are not considered 
    % as the BCG of a cluster (\mhalo{}$\simgt 10^{14}M_{\star}$) \alexie{CHECK}. 
    % Only a small fraction of the BCGs in the \rbcg{} sample belong to very 
    % massive clusters where the strongest photometric evidence of an ICL component is 
    % often found (\mhalo{}$\simgt 10^{15}M_{\star}$, e.g. \citealt{Presotto2014, 
    % Burke2015}). 
    % The virgo cluster is a good  local analog of the typical galaxy in our sample.

    % Ultra-deep images show that the stellar halo of the BCG smoothly extends beyond 
    % 100 kpc, while the ICL only becomes important outside that radius and is dominated 
    % by many individual tidal features (e.g. \citealt{Mihos2016}).
    % Therefore, it is highly unlikely that out main results are driven by the ICL 
    % component.

    % At the imaging depth of HSC and out to 100 kpc, the \mden{} profiles of massive 
    % galaxies vary smoothly and we find no evidence for a distinctive ICL component. 
    % Although the rising stellar velocity dispersion in the outskirt of massive BCG
    % has been used as evidence of a kinematically separated ICL component (e.g. 
    % \citealt{Dressler1979, Carter1999, Kelson2002, Bender2015, Longobardi2015}), 
    % we think it is reasonable to treat the stellar halo of BCG and potential ICL as 
    % an integrated component. 
    % They both carry important information regarding the assembly of central galaxy 
    % and its dark matter halo. 
    % In recent years, we can start to investigate the origin and evolution of ICL using 
    % simulations where physical separation of ICL is possible
    % (e.g. \citealt{SommerLarsen2005, Murante2007, Martel2012, Cui2014, Cooper2015, 
    % Harris2017}). 
    % It will be interesting to perform detailed comparisons between these simulations 
    % and deep HSC observations to look into the contributions from different stellar 
    % components to the halo of massive galaxy.

@@
